Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-25 fmics/paper.tex
Correct the definition of tap
Explain why we have both RS and output

%We describe the more realistic (second phase) model here.
Table~\ref{tab:descriptions} lists the HOL functions we defined in the second phase along with their intended meanings.
The arrangement of the slices is described by functions $\mathsf{input}\;n$ and $\mathsf{tap}\;n\;x$.
The read delay of a slice is modeled by $\mathsf{delay}\;n$.
Each slice is modeled by three functions: $\mathsf{SR}\;D\;n\;m\;t$ represents the value of each cell of the slice's shift register, $\mathsf{source}\;D\;n\;m\;t$ represents the direct input of each cell, and $\mathsf{output}\;D\;n\;x\;t$ represents the value of the slice's output at its taps.
The $\mathsf{RS}\;D\;n\;t$ models the running sums and $\mathsf{update\_time}\;n\;t$ checks if it is the time to refresh the contents of slice $n$.
{\bf should we explain why we have both output function and RS?}

@@

\begin{figure}
\caption{
Definitions of the HOL functions comprising our model of the SRS structure.
\(\mathsf{tap}\) and \(\mathsf{input}\) are defined to match Figure~\ref{fig:srs}, %counting positions within a shift register from $0$.
Slice $0$ is a fake slice representing the SRS input; this enables a succinct definition of $\mathsf{source}$.
%The definition of $\mathsf{input}$ when $n=0$ or when $n>6$ does not change the structure represented, so we use definitions convenient for proving theorems.
%A similar comment applies to other definitions when $n$, representing a slice number, is $0$, or when $x$, representing a shift register position, is above $1$.
\label{fig:definitions}}
\begin{align*}
\mathsf{tap}\;0\;0&=0&\mathsf{tap}\;0\;1&=0\\
\mathsf{tap}\;1\;0&=1-1&\mathsf{tap}\;1\;1&=2-1\\
\mathsf{tap}\;2\;0&=8-1&\mathsf{tap}\;2\;1&=16-1\\
&\dots&\mathsf{tap}\;6\;x&=128-1\quad\text{(where $x>0$)}\\\\
\mathsf{input}\;0&=(0,0)&\mathsf{input}\;1&=(0,0)\\
\mathsf{input}\;2&=(0,0)&\mathsf{input}\;3&=(1,1)\\
\mathsf{input}\;4&=(3,0)&\mathsf{input}\;5&=(4,0)\\
\mathsf{input}\;6&=(4,1)&\mathsf{input}\;n&=(n-1,0)\quad\text{(where $n>6$)}
\end{align*}
\begin{align*}
\mathsf{delay}\;0&=1\\
\mathsf{delay}\;n&=\mathsf{delay}\;n'\times((\mathsf{tap}\;n'\;x)+1)\\
&\qquad\text{where $(n',x)=\mathsf{input\;n}$ (and $n>0$)}
\end{align*}
\begin{align*}
\mathsf{update\_time}\;n\;t&\iff(t\operatorname{mod}\mathsf{delay}\;n=0)
\end{align*}
\begin{align*}
\mathsf{source}\;D\;n\;0\;t&=\mathsf{output}\;D\;n'\;x\;t\quad\text{where $(n',x)=\mathsf{input\;n}$}\\
\mathsf{source}\;D\;n\;m\;t&=\;\mathsf{SR}\;D\;n\;(m-1)\;\quad\text{(where $m>0$)}
\end{align*}
\begin{align*}
\mathsf{output}\;D\;0\;x\;t&=D\;t\\
\mathsf{output}\;D\;n\;x\;0&=0\\
\mathsf{output}\;D\;n\;x\;t&=
\text{if $\mathsf{update\_time}\;n\;t$}\\
&\qquad\text{then }((\mathsf{output}\;D\;n\;x\;(t-1))+(\mathsf{source}\;D\;n\;0\;(t-1)))-(\mathsf{SR}\;D\;n(\mathsf{tap}\;n\;x)\;(t-1))\\
&\qquad\text{else }\mathsf{output}\;D\;n\;x\;(t-1)\qquad\text{(where $t>0$)}
\end{align*}
\begin{align*}
\mathsf{SR}\;D\;n\;m\;0&=0\\
\mathsf{SR}\;D\;n\;m\;t&=\text{if $\mathsf{update\_time}\;n\;t$}\\
&\qquad\text{then }\mathsf{source}\;D\;n\;m\;(t-1)\\
&\qquad\text{else }\mathsf{SR}\;D\;n\;m\;t\qquad\text{(where $t>0$)}
\end{align*}
\begin{align*}
\mathsf{RS}\;D\;n\;t&=\mathsf{output}\;D\;\left(\left\lfloor\frac{n}{2}\right\rfloor+1\right)\;(n\operatorname{mod}2)
\end{align*}
\end{figure}

>>>>

%We describe the more realistic (second phase) model here.
Table~\ref{tab:descriptions} lists the HOL functions we defined in the second phase along with their intended meanings.
The arrangement of the slices is described by functions $\mathsf{input}\;n$ and $\mathsf{tap}\;n\;x$.
The read delay of a slice is modeled by $\mathsf{delay}\;n$.
Each slice is modeled by three functions: $\mathsf{SR}\;D\;n\;m\;t$ represents the value of each cell of the slice's shift register, $\mathsf{source}\;D\;n\;m\;t$ represents the direct input of each cell, and $\mathsf{output}\;D\;n\;x\;t$ represents the value of the slice's output at its taps.
The function $\mathsf{RS}\;D\;n\;t$ models the running sums and $\mathsf{update\_time}\;n\;t$ checks if it is time to refresh the contents of a slice.
We have both $\mathsf{RS}$ and $\mathsf{output}$ functions, though $\mathsf{RS}$ is easily defined in terms of $\mathsf{output}$, because $\mathsf{RS}$ represents a whole SRS output (indexed by a single number), whereas $\mathsf{output}$ represents an individual slice output (indexed by slice and tap).
By separating $\mathsf{RS}$ and $\mathsf{output}$, we allow for designs where some slice outputs are not SRS outputs, but may still be used internally between slices.

@@

\begin{figure}
\caption{
Definitions of the HOL functions comprising our model of the SRS structure.
\(\mathsf{tap}\) and \(\mathsf{input}\) are defined to match Figure~\ref{fig:srs}, %counting positions within a shift register from $0$.
Slice $0$ is a fake slice representing the SRS input; this enables a succinct definition of $\mathsf{source}$.
%The definition of $\mathsf{input}$ when $n=0$ or when $n>6$ does not change the structure represented, so we use definitions convenient for proving theorems.
%A similar comment applies to other definitions when $n$, representing a slice number, is $0$, or when $x$, representing a shift register position, is above $1$.
\label{fig:definitions}}
\begin{align*}
\mathsf{tap}\;0\;0&=0&\mathsf{tap}\;0\;x&=0\\
\mathsf{tap}\;1\;0&=1-1&\mathsf{tap}\;1\;x&=2-1\\
\mathsf{tap}\;2\;0&=8-1&\mathsf{tap}\;2\;x&=16-1\\
&\dots&\mathsf{tap}\;6\;x&=128-1\quad\text{(where each $x>0$)}\\\\
\mathsf{input}\;0&=(0,0)&\mathsf{input}\;1&=(0,0)\\
\mathsf{input}\;2&=(0,0)&\mathsf{input}\;3&=(1,1)\\
\mathsf{input}\;4&=(3,0)&\mathsf{input}\;5&=(4,0)\\
\mathsf{input}\;6&=(4,1)&\mathsf{input}\;n&=(n-1,0)\quad\text{(where $n>6$)}
\end{align*}
\begin{align*}
\mathsf{delay}\;0&=1\\
\mathsf{delay}\;n&=\mathsf{delay}\;n'\times((\mathsf{tap}\;n'\;x)+1)\\
&\qquad\text{where $(n',x)=\mathsf{input\;n}$ (and $n>0$)}
\end{align*}
\begin{align*}
\mathsf{update\_time}\;n\;t&\iff(t\operatorname{mod}\mathsf{delay}\;n=0)
\end{align*}
\begin{align*}
\mathsf{source}\;D\;n\;0\;t&=\mathsf{output}\;D\;n'\;x\;t\quad\text{where $(n',x)=\mathsf{input\;n}$}\\
\mathsf{source}\;D\;n\;m\;t&=\;\mathsf{SR}\;D\;n\;(m-1)\;\quad\text{(where $m>0$)}
\end{align*}
\begin{align*}
\mathsf{output}\;D\;0\;x\;t&=D\;t\\
\mathsf{output}\;D\;n\;x\;0&=0\\
\mathsf{output}\;D\;n\;x\;t&=
\text{if $\mathsf{update\_time}\;n\;t$}\\
&\qquad\text{then }((\mathsf{output}\;D\;n\;x\;(t-1))+(\mathsf{source}\;D\;n\;0\;(t-1)))-(\mathsf{SR}\;D\;n(\mathsf{tap}\;n\;x)\;(t-1))\\
&\qquad\text{else }\mathsf{output}\;D\;n\;x\;(t-1)\qquad\text{(where $t>0$)}
\end{align*}
\begin{align*}
\mathsf{SR}\;D\;n\;m\;0&=0\\
\mathsf{SR}\;D\;n\;m\;t&=\text{if $\mathsf{update\_time}\;n\;t$}\\
&\qquad\text{then }\mathsf{source}\;D\;n\;m\;(t-1)\\
&\qquad\text{else }\mathsf{SR}\;D\;n\;m\;t\qquad\text{(where $t>0$)}
\end{align*}
\begin{align*}
\mathsf{RS}\;D\;n\;t&=\mathsf{output}\;D\;\left(\left\lfloor\frac{n}{2}\right\rfloor+1\right)\;(n\operatorname{mod}2)
\end{align*}
\end{figure}
